---
output: github_document
bibliography: swhids.bib
nocite: '@*'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# swhidit

<!-- badges: start -->
<!-- badges: end -->

The goal of swhidit is to ...

## Installation

*TODO*: You can install the released version of swhidit from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("swhidit")
```

You can install the development version of swhidit from [GitHub](https://github.com/nfultz/swhidit) with:

``` r
remotes::install_github("nfultz/swhidit")
```


## Example

This is a basic example which shows you how to fetch SWHIDs for all attached packages in your session: 

```{r example, warning=FALSE}
library(swhidit)
library(jsonlite)
swhidit()
```

which generates a bibtex database:

```{r, echo=FALSE, comment=NA}
cat(readLines("swhids.bib"), sep='\n')
```

which is then rendered using the appropriate tools:

# References

